---
header-includes:
    \renewcommand{\familydefault}{\sfdefault}
output:
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: no
    toc_float:
      collapsed: yes
  pdf_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=8,fig.height=2,      
                      echo=FALSE, warning=FALSE, message=FALSE)

```

```{r echo=FALSE}
library(ggplot2)
library(tidyverse)

source("SWB231_data_load.R")

pth <- file.path(getwd(), "data", "surveyvariabletranslation.csv")
variable_transformation <- read.csv(pth, header=TRUE)

generate_current_question <- function(question_preface) {
  current_question <- satisfaction_survey %>%
  select(
    "Q01_Org_Name",starts_with(question_preface)
  ) %>% 
  na.omit()
  return(current_question)
}

generate_summary_plot <- function(question_preface, title) {
  
  current_question <- generate_current_question(question_preface)
  
  conf_min <- mean(current_question[[2]]) - sd(current_question[[2]])
  conf_max <- mean(current_question[[2]]) + sd(current_question[[2]])

  confidence_line <- data.frame(x = c(conf_min, conf_max),
                              y = c(0.25, 0.25))

  likert_default <- data.frame(x = c(1,2,3,4,5),
                  y = c(0.1,0.1,0.1,0.1,0.1))


  number_line <- likert_default %>% 
    ggplot(aes(x,y)) +
    geom_point(aes(size=10), shape=1, colour = "#1a1a1a") +
    labs(title = title,x = "Rank (1 = Lowest, 5 = Highest)") +
    theme(legend.position="none", 
            rect = element_blank(),
            panel.grid = element_blank(),
            axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y=element_blank()
            ) +
    coord_fixed(ratio = 3) +
    geom_point(aes(x=mean(current_question[[2]]), y=0.1, size = 10), colour="#7045ff") +
    geom_segment(aes(x = confidence_line$x[1], y = confidence_line$y[1], xend = confidence_line$x[2], yend = confidence_line$y[2]), colour="#7045ff") +
    geom_point(aes(x=confidence_line$x[1], y = confidence_line$y[1], size = 10), shape = "|", colour="#7045ff") +
    geom_point(aes(x=confidence_line$x[2], y = confidence_line$y[2], size = 10), shape = "|", colour="#7045ff") +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.05, 
        label = "",
        color = "white",
        fontface = 2,
        size = 1
    ) +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.15, 
        label = paste("Average",round(mean(current_question[[2]]),2)),
        color = "#1a1a1a",
        fontface = 2,
        size = 3
    ) +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.3, 
        label = "68% Confidence Range",
        color = "#1a1a1a",
        fontface = 2,
        size = 3
    )
  
    return(number_line)
}

generate_count_plot <- function(question_preface, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  current_question <- generate_current_question(question_preface)

  count_table <- data_frame(rank = c(5,4,3,2,1), count = c(0,0,0,0,0))

  for(rank in count_table$rank) {
    count_table$count[count_table$rank == rank] <- length(which(current_question[[2]]==rank))
  }

  count_table <- count_table %>% 
    mutate(
      percent = count/nrow(current_question),
      display = row_number()
    )

  overview_dataframe <- count_table

count_barplot <- ggplot(overview_dataframe, aes_string(x = colnames(overview_dataframe)[1], y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = title,y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )
  
    return(count_barplot)
}

generate_yes_no_plot <- function(question_preface, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  current_question <- generate_current_question(question_preface)

  yes_no_column <- current_question[2]

  yes_no_column <- yes_no_column %>% 
    mutate(
      yes_no = ifelse(yes_no_column[row_number(),1] == 1, "Yes", "No")
    ) %>%
    select(yes_no)

  yes_no_table <- data_frame(rank = c("Yes","No"), count = c(0,0))

  for(rank in yes_no_table$rank) {
    yes_no_table$count[yes_no_table$rank == rank] <- length(which(yes_no_column[[1]]==rank))
  }

  yes_no_table <- yes_no_table %>% 
    mutate(
      percent = count/nrow(current_question),
      display = row_number()
    )

  overview_dataframe <- yes_no_table

count_barplot <- ggplot(overview_dataframe, aes_string(x = colnames(overview_dataframe)[1], y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = title,y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )
  
    return(count_barplot)
}

generate_open_response_list <- function(question_preface, ignore_score = FALSE) {
  
  current_question <- generate_current_question(question_preface)
  
  paste0(cat("\n<h3 style=\"text-decoration: none; font-weight: normal;\">Comments on This Question</h3>"))
  
  for(numrow in 1:nrow(current_question)) {
    score_text = ""
    if(!ignore_score) {
      score_text <- paste0("\n\n<span style=\"color: #1a1a1a;\">Score:", current_question[[numrow,2]],"</span>")
    }
    if(!current_question[[numrow,length(current_question)]] %in% c("NA", "n/a", "N/A")) {
      paste0(cat("\n<div style=\"padding: 0 2em; margin-bottom: 0.5em;\"><div style=\"font-size: 90%; border-bottom: 1px solid #e0e0e0; border-color: #e0e0e0;\">\n<span style=\"color: #7045ff;\">",current_question[[numrow,1]],"</span>", score_text, "\n<div style=\"padding: 1em;\">", current_question[[numrow,length(current_question)]],"</div>\n</div></div>"), sep = "\n\n\n\n")
    }
  }
}



generate_question_overview_dataframe <- function(question_number, original_data_frame) {
  question_overview <- original_data_frame %>%
  select(starts_with(paste(question_number, '_', sep=""))) %>%
  pivot_longer(
    everything(), 
    names_to = "answer_type", 
    names_prefix = paste(question_number, '_', sep=""),
    values_to = "count") %>%
  filter(count != 0 ) %>%
  group_by(answer_type) %>%
  summarize(
    count = sum(count),
    percent = count/nrow(original_data_frame)
  )

return(question_overview)
}

generate_question_type_dataframe <- function(question_preface) {
  
  current_question <- generate_current_question(question_preface)
  
  select_question <- current_question %>%
  select(contains("_Type_")) %>%
  pivot_longer(
    everything(), 
    names_to = "answer_type", 
    names_prefix = paste(question_preface, '_', sep=""),
    values_to = "count") %>%
  filter(count != 0 ) %>%
  group_by(answer_type) %>%
  summarize(
    count = sum(count),
    percent = count/nrow(current_question)
  )

question_type_translations <- variable_transformation %>%
  filter(variable_name %in% select_question[[1]])
question_type_translations <- question_type_translations %>% arrange(variable_name)

select_question <- select_question %>%
  mutate(
    answer_type = question_type_translations$translation[question_type_translations$variable_name == answer_type]
  )

return(select_question)
}

generate_question_type_overview_plot <- function(question_preface, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  overview_dataframe <- generate_question_type_dataframe(question_preface)
  
  overview_barplot <- ggplot(overview_dataframe, aes_string(x = paste0("reorder(",colnames(overview_dataframe)[1],", ",colnames(overview_dataframe)[3],")"), y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = title,y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )
  
  return(overview_barplot)
}

satisfaction_survey <- results_2023 %>%
  select(
    "Q01_Org_Name",starts_with("SQ")
  )

satisfaction_survey <- satisfaction_survey %>%
  mutate_at(vars(contains("open_response")), ~replace_na(., "NA"))
  

```
<style>
body {
color: #1a1a1a;
font-family: Calibre, Arial, sans-serif;
}
h1, h2, h3 {
color: #7045ff;
}
h3 {
font-weight: bold;
text-decoration: underline;
}
</style>

# H2H Satisfaction Survey Results Overview

### Question 1

Overall, how satisfied are you with the H2H Network to date?

Please rank 1 not at all satisfied and 5 is very satisfied.

```{r echo=FALSE, results = 'asis'}

cat("</br>")

question_preface <- "SQ01"

generate_summary_plot("SQ01", "Overall Satisfaction with H2H Services")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot("SQ01", "Overall Satisfaction with H2H Services Rank Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list("SQ01")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")


```

### Question 2

How engaged have you been in the network , either bilaterally with other members, or through the network’s processes or activities?

Please rank 1 is not at all involved and 5 is very involved. Please select how you have been engaged.

- Board member  
- Regularly participating in calls and workshops 
- engaging with the Communications Community of Practice of the Impact and Learning Advisory Group  
- Participating in H2H Network-organized events at HNPW or elsewhere 
- Other (please specify) 


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ02"

generate_summary_plot(question_preface, "Overall Level of Engagement")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot(question_preface, "Overall Level of Engagement Rank Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "How Members Have Been Engaged", offset_1 = 0.81)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 3

Have you collaborated with other members of the network?

If yes, was it a formal collaboration (might be a joint project or funding proposal) or an informal collaboration (might be ad-hoc information sharing) For example, a formal collaboration might be a joint project or funding proposal, an informal collaboration might be ad-hoc information sharing. 

- Please share details. This is extremely useful information for us! 

```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ03"

cat("</br>")
cat("</br>")

generate_yes_no_plot(question_preface, "Have Collaborated With Other Network Members")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "How Members Have Collaborated Together", offset_1 = 0.81)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 4

If you have collaborated with other members, did the H2H Network core team facilitate this collaboration?

Please share details in the comment box 

```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ04"

current_question <- generate_current_question(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "How Did H2H Core Help with Collaboration?")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 5

Which internal channels do you use to engage with the network? (select all that apply) 

- 1:1 calls or email exchanges with the core team 
- Monthly members’ updates/ general emails  
- Internal members’ hub (SharePoint) 
- Community of Practice slack channel 
- Crisis watch calls 
- Other (please specify)


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ05"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "Which Internal Channels Were Used to Engage?")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 6

Would you like to propose any new topics for communities of practice, for learning webinars or workshops?  


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ06"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 7

Would you like to make any other suggestions concerning the future development of members’ services?  


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ07"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 8

Have you previously applied to the H2H Fund? 


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ08"

cat("</br>")
cat("</br>")

generate_yes_no_plot(question_preface, "Have Previously Applied to H2H Fund")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 9

If you have not applied to the H2H Fund, what are the main reasons?

- The process around accessing funding is unclear to you 
- The crisis covered by the Fund activations do not align with your operational priorities and capacities 
- Your organization had other sources of funding for your response to the crisis covered by the Fund 
- The timeframe to submit a project proposal is too short  
- The process around submitting an application (narrative proposal, budget, workplan…) is too complex 
- The Due Diligence Assessment required to access the fund is too complex or time-consuming 
- The amount allocated is too small 
- The timeframe to implemented funded projects is too short 
- Other (please comment) 



```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ09"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "Why did you not apply to the H2H Fund?")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 10

If you applied to the H2H Fund but were unsuccessful, was the feedback you receive useful to help you understand the rationale and improve future applications?


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ10"

cat("</br>")
cat("</br>")

generate_yes_no_plot(question_preface, "H2H Fund Rejection Feedback Was Useful")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 11

How would you assess the transparency of the decision-making process by the H2H Grant Panel with regards to the selection of project proposals?

1 is not at all transparent and 5 is very transparent


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ11"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_summary_plot(question_preface, "Overall Level of Transparency by H2H Grant Panel")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot(question_preface, "Overall Level of Transparency by H2H Grant Panel Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 12

If you received a grant, how would you rate the support provided by the core team throughout the Fund activation process, both administrative and programmatic?

1 is not at all helpful and 5 is very helpful


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ12"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_summary_plot(question_preface, "Overall Quality of Support by H2H Core Team on Fund Activation Process")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot(question_preface, "Overall Quality of Support by H2H Core TEam on Fund Activation Process Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 13

Would you like to make any other suggestions concerning the future development of the fund or the directions it could take?


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ13"

cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 14

Overall, do you believe there is greater awareness of the network than one year ago? Please share details in the comment box (operational agencies at HQ or response levels; donors; local and national actors)


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ14"

cat("</br>")
cat("</br>")

generate_yes_no_plot(question_preface, "Believe There is Greater Awareness of H2H Than One Year Ago")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 15

How do you communicate to operational agencies, donors and local/ national actors about the H2H Network and your role as a member?


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ15"

cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 16

From your perspective, which activities most effectively support external engagement for the network and the H2H approach?

- External communications 
- Events at global/HQ levels 
- Deployment 
- Other 

```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ16"

SQ16 <- generate_current_question(question_preface)

SQ16 <- SQ16 %>%
  mutate(
    SQ16_Rank_External_Engagement_Approach_Deployment_Rank = 0,
    SQ16_Rank_External_Engagement_Approach_External_Rank = 0,
    SQ16_Rank_External_Engagement_Approach_Events_Rank = 0
  )

for(row_num in 1:nrow(SQ16)) {
  order_list <- unlist(strsplit(SQ16[row_num,2], ","))
  rank_list <- match(c("Deployment ", "Events at global/HQ levels ", "External communications "), order_list)
  SQ16[row_num,4] <- 3 - rank_list[1] + 1
  SQ16[row_num,5] <- 3 - rank_list[2] + 1
  SQ16[row_num,6] <- 3 - rank_list[3] + 1
}


generate_rank_plot <- function(question_vector, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  current_question <- question_vector

  count_table <- data_frame(rank = c(3,2,1), count = c(0,0,0))

  for(rank in count_table$rank) {
    count_table$count[count_table$rank == rank] <- length(which(current_question==rank))
  }

  count_table <- count_table %>% 
    mutate(
      percent = count/length(current_question),
      display = row_number()
    )

  overview_dataframe <- count_table

count_barplot <- ggplot(overview_dataframe, aes_string(x = colnames(overview_dataframe)[1], y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = paste(title, " (Average Rank: ", round(mean(current_question),2), ", 1 = Low, 3 = High)"),y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )

return(count_barplot)
  
}

cat("</br>")
cat("</br>")

generate_rank_plot(SQ16$SQ16_Rank_External_Engagement_Approach_Deployment_Rank, "Rank of Deployment in Supporting Engagement")

cat("</br>")
cat("</br>")

generate_rank_plot(SQ16$SQ16_Rank_External_Engagement_Approach_External_Rank, "Rank of External Comms in Supporting Engagement")

cat("</br>")
cat("</br>")

generate_rank_plot(SQ16$SQ16_Rank_External_Engagement_Approach_Events_Rank, "Rank of Events in Supporting Engagement")

cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 17

Which external channels do you use to engage with the network?

- Social media 
- Website 
- Public newsletter 
- Events 
- Other

```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ17"

cat("</br>")

generate_question_type_overview_plot(question_preface, "External Channels Used to Engage With The Network?")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 18

From your perspective, in the context of fund activations, which activities most effectively support external engagement?

- Communications package 
- Brokering with stakeholders (end-users, donors, partners…) 
- Deployment 
- Other


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ18"

cat("</br>")

generate_question_type_overview_plot(question_preface, "Activities Which Support External Engagement")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 19

Would you like to make any other suggestions concerning the H2H Network’s brokering and facilitation activities?


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ19"

cat("</br>")

generate_open_response_list(question_preface, TRUE)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```