---
header-includes:
    \renewcommand{\familydefault}{\sfdefault}
output:
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: no
    toc_float:
      collapsed: yes
  pdf_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=8,fig.height=2,      
                      echo=FALSE, warning=FALSE, message=FALSE)

```

```{r echo=FALSE}
library(ggplot2)
library(tidyverse)

source("SWB231_data_load.R")

pth <- file.path(getwd(), "data", "surveyvariabletranslation.csv")
variable_transformation <- read.csv(pth, header=TRUE,encoding = "latin1")

generate_current_question <- function(question_preface) {
  current_question <- satisfaction_survey %>%
  select(
    "Q01_Org_Name",starts_with(question_preface)
  ) %>% 
  na.omit()
  return(current_question)
}

generate_summary_plot <- function(question_preface, title) {
  
  current_question <- generate_current_question(question_preface)
  
  conf_min <- mean(current_question[[2]]) - sd(current_question[[2]])
  conf_max <- mean(current_question[[2]]) + sd(current_question[[2]])

  confidence_line <- data.frame(x = c(conf_min, conf_max),
                              y = c(0.25, 0.25))

  likert_default <- data.frame(x = c(1,2,3,4,5),
                  y = c(0.1,0.1,0.1,0.1,0.1))


  number_line <- likert_default %>% 
    ggplot(aes(x,y)) +
    geom_point(aes(size=10), shape=1, colour = "#1a1a1a") +
    labs(title = title,x = "Rank (1 = Lowest, 5 = Highest)") +
    theme(legend.position="none", 
            rect = element_blank(),
            panel.grid = element_blank(),
            axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y=element_blank()
            ) +
    coord_fixed(ratio = 3) +
    geom_point(aes(x=mean(current_question[[2]]), y=0.1, size = 10), colour="#7045ff") +
    geom_segment(aes(x = confidence_line$x[1], y = confidence_line$y[1], xend = confidence_line$x[2], yend = confidence_line$y[2]), colour="#7045ff") +
    geom_point(aes(x=confidence_line$x[1], y = confidence_line$y[1], size = 10), shape = "|", colour="#7045ff") +
    geom_point(aes(x=confidence_line$x[2], y = confidence_line$y[2], size = 10), shape = "|", colour="#7045ff") +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.05, 
        label = "",
        color = "white",
        fontface = 2,
        size = 1
    ) +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.15, 
        label = paste("Average",round(mean(current_question[[2]]),2)),
        color = "#1a1a1a",
        fontface = 2,
        size = 3
    ) +
    annotate(
        "text", 
        x = mean(current_question[[2]]), 
        y = 0.3, 
        label = "68% Confidence Range",
        color = "#1a1a1a",
        fontface = 2,
        size = 3
    )
  
    return(number_line)
}

generate_count_plot <- function(question_preface, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  current_question <- generate_current_question(question_preface)

  count_table <- data_frame(rank = c(5,4,3,2,1), count = c(0,0,0,0,0))

  for(rank in count_table$rank) {
    count_table$count[count_table$rank == rank] <- length(which(current_question[[2]]==rank))
  }

  count_table <- count_table %>% 
    mutate(
      percent = count/nrow(current_question),
      display = row_number()
    )

  overview_dataframe <- count_table

count_barplot <- ggplot(overview_dataframe, aes_string(x = colnames(overview_dataframe)[1], y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = title,y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )
  
    return(count_barplot)
}

generate_open_response_list <- function(question_preface) {
  
  current_question <- generate_current_question(question_preface)
  
  paste0(cat("\n<h3 style=\"text-decoration: underline; font-weight: bold;\">Comments on This Question</h3>"))
  
  for(numrow in 1:nrow(current_question)) {
    if(!current_question[[numrow,length(current_question)]] %in% c("NA", "n/a", "N/A")) {
      paste0(cat("\n<div style=\"padding: 0 2em; margin-bottom: 0.5em;\"><div style=\"font-size: 90%; border-bottom: 1px solid #e0e0e0; border-color: #e0e0e0;\">\n<span style=\"color: #7045ff;\">",current_question[[numrow,1]],"</span>\n\n<span style=\"color: #1a1a1a;\">Score:", current_question[[numrow,2]],"</span>","\n<div style=\"padding: 1em;\">", current_question[[numrow,length(current_question)]],"</div>\n</div></div>"), sep = "\n\n\n\n")
    }
  }
}



generate_question_overview_dataframe <- function(question_number, original_data_frame) {
  question_overview <- original_data_frame %>%
  select(starts_with(paste(question_number, '_', sep=""))) %>%
  pivot_longer(
    everything(), 
    names_to = "answer_type", 
    names_prefix = paste(question_number, '_', sep=""),
    values_to = "count") %>%
  filter(count != 0 ) %>%
  group_by(answer_type) %>%
  summarize(
    count = sum(count),
    percent = count/nrow(original_data_frame)
  )

return(question_overview)
}

generate_question_type_dataframe <- function(question_preface) {
  
  current_question <- generate_current_question(question_preface)
  
  select_question <- current_question %>%
  select(contains("_Type_")) %>%
  pivot_longer(
    everything(), 
    names_to = "answer_type", 
    names_prefix = paste(question_preface, '_', sep=""),
    values_to = "count") %>%
  filter(count != 0 ) %>%
  group_by(answer_type) %>%
  summarize(
    count = sum(count),
    percent = count/nrow(current_question)
  )

question_type_translations <- variable_transformation %>%
  filter(variable_name %in% select_question[[1]])
question_type_translations <- question_type_translations %>% arrange(variable_name)

select_question <- select_question %>%
  mutate(
    answer_type = question_type_translations$translation[question_type_translations$variable_name == answer_type]
  )

return(select_question)
}

generate_question_type_overview_plot <- function(question_preface, title, offset_1 = 0.83, offset_2 = 0.92) {
  
  overview_dataframe <- generate_question_type_dataframe(question_preface)
  
  overview_barplot <- ggplot(overview_dataframe, aes_string(x = paste0("reorder(",colnames(overview_dataframe)[1],", ",colnames(overview_dataframe)[3],")"), y = colnames(overview_dataframe)[3])) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.x = element_blank()
  ) +
  geom_col(
    aes(y=1),
    color=NA,
    fill = "grey",
    alpha=.15
  ) +
  geom_col(
    color=NA,
    fill = "#7045ff"
  ) +
  coord_flip() +
  labs(title = title,y = "Count (Percent of Respondents)") +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_1, 
      label = overview_dataframe[[2]],
      color = "#1a1a1a",
      fontface = 2,
      size = 3.5
  ) +
  annotate(
      "text", 
      x = overview_dataframe[[1]], 
      y = offset_2, 
      label = sprintf("(%0.2f%%)", overview_dataframe[[3]]*100),
      color = "#1a1a1a",
      size = 3.5
  )
  
  return(overview_barplot)
}

satisfaction_survey <- results_2023 %>%
  select(
    "Q01_Org_Name",starts_with("SQ")
  )

satisfaction_survey <- satisfaction_survey %>%
  mutate_at(vars(contains("open_response")), ~replace_na(., "NA"))
  

```
<style>
body {
color: #1a1a1a;
font-family: Calibre, Arial, sans-serif;
}
h1, h2, h3 {
color: #7045ff;
}
</style>

# H2H Satisfaction Survey Results Overview
Summary Results Report by Olivia McCargar


### Question 1

Overall, how satisfied are you with the H2H Network to date?

Please rank 1 not at all satisfied and 5 is very satisfied.

```{r echo=FALSE, results = 'asis'}

cat("</br>")

question_preface <- "SQ01"

generate_summary_plot("SQ01", "Overall Satisfaction with H2H Services")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot("SQ01", "Overall Satisfaction with H2H Services Rank Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_summary_plot("SQ01", "Overall Satisfaction with H2H Services")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list("SQ01")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")


```

### Question 2

How engaged have you been in the network , either bilaterally with other members, or through the network’s processes or activities?

Please rank 1 is not at all involved and 5 is very involved. Please select how you have been engaged.

- Board member  
- Regularly participating in calls and workshops 
- engaging with the Communications Community of Practice of the Impact and Learning Advisory Group  
- Participating in H2H Network-organized events at HNPW or elsewhere 
- Other (please specify) 


```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ02"

generate_summary_plot(question_preface, "Overall Level of Engagement")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_count_plot(question_preface, "Overall Level of Engagement Rank Count")

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "How Members Have Been Engaged", offset_1 = 0.81)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```

### Question 3

Have you collaborated with other members of the network?

If yes, was it a formal collaboration (might be a joint project or funding proposal) or an informal collaboration (might be ad-hoc information sharing) For example, a formal collaboration might be a joint project or funding proposal, an informal collaboration might be ad-hoc information sharing. 

- Please share details. This is extremely useful information for us! 

```{r echo=FALSE, results = 'asis'}

question_preface <- "SQ03"

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_question_type_overview_plot(question_preface, "How Members Have Collaborated Together", offset_1 = 0.81)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

generate_open_response_list(question_preface)

cat("</br>")
cat("</br>")
cat("</br>")
cat("</br>")

```