---
header-includes:
    \renewcommand{\familydefault}{\sfdefault}
output:
  pdf_document:
    toc: no
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: no
    toc_float:
      collapsed: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=8,fig.height=2,      
                      echo=FALSE, warning=FALSE, message=FALSE)

```

```{r echo=FALSE}
library(ggplot2)
library(tidyverse)

source("SWB231_data_load.R")

satisfaction_survey <- results_2023 %>%
  select(
    "Q01_Org_Name",starts_with("SQ")
  )

```
<style>
body {
color: #1a1a1a;
font-family: Calibre, Arial, sans-serif;
}
h1, h2, h3 {
color: #7045ff;
}
</style>

# <span style="text-align: center;">H2H Satisfaction Survey Results Overview</span>
<span style="text-align: center;">Summary Results Report by Olivia McCargar</span>


### Question 1

How engaged have you been in the network, either bilaterally with other members, or through the network’s processes or activities?

Please rank 1 is not at all involved and 5 is very involved.  

```{r echo=FALSE}

SQ01 <- satisfaction_survey %>%
  select(
    "Q01_Org_Name",starts_with("SQ01")
  ) %>% 
  na.omit()

conf_min <- mean(SQ01$SQ01_H2H_Network_Satisfaction) - sd(SQ01$SQ01_H2H_Network_Satisfaction)
conf_max <- mean(SQ01$SQ01_H2H_Network_Satisfaction) + sd(SQ01$SQ01_H2H_Network_Satisfaction)

confidence_line <- data.frame(x = c(conf_min, conf_max),
                              y = c(0.25, 0.25))

likert_default <- data.frame(x = c(1,2,3,4,5),
                y = c(0,0,0,0,0))

number_line <- likert_default %>% 
  ggplot(aes(x,y)) +
  geom_point(aes(size=10), shape=1, colour = "#1a1a1a") +
  theme(legend.position="none", 
            rect = element_blank(),
            panel.grid = element_blank(),
            axis.title = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y=element_blank()
            ) +
  coord_fixed(ratio = 3) +
  geom_point(aes(x=mean(SQ01$SQ01_H2H_Network_Satisfaction), y=0, size = 10), colour="#7045ff") +
  geom_segment(aes(x = confidence_line$x[1], y = confidence_line$y[1], xend = confidence_line$x[2], yend = confidence_line$y[2]), colour="#7045ff") +
  geom_point(aes(x=confidence_line$x[1], y = confidence_line$y[1], size = 10), shape = "|", colour="#7045ff") +
  geom_point(aes(x=confidence_line$x[2], y = confidence_line$y[2], size = 10), shape = "|", colour="#7045ff") +
  annotate(
      "text", 
      x = mean(SQ01$SQ01_H2H_Network_Satisfaction), 
      y = 0.5, 
      label = "",
      color = "white",
      fontface = 2,
      size = 1
  ) +
  annotate(
      "text", 
      x = mean(SQ01$SQ01_H2H_Network_Satisfaction), 
      y = 0.1, 
      label = paste("Average",round(mean(SQ01$SQ01_H2H_Network_Satisfaction),2)),
      color = "#1a1a1a",
      fontface = 2,
      size = 3
  ) +
  annotate(
      "text", 
      x = mean(SQ01$SQ01_H2H_Network_Satisfaction), 
      y = 0.3, 
      label = "68% Confidence Range",
      color = "#1a1a1a",
      fontface = 2,
      size = 3
  )

number_line

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
